Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
min max date
lc

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017, 2018 and
2019. Adult female caribou were immobilized and fitted with global positioning
system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
to remove all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
proportion of marked adult females was ~10% of all adult females and ~5% of all
individuals in the herd. We assumed these individuals were randomly distributed
throughout the population.

## Landscape data and habitat classification
Land cover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification included nine habitat
types at 30 m resolution. We reclassified the land cover types into three
categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broad leaf forest, and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.

>>>>

## Caribou location data
We used GPS location data collected from Fogo Island caribou in between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Adult female caribou were immobilized and fitted with global positioning
system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
to remove all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
proportion of marked adult females was ~10% of all adult females and ~5% of all
individuals in the herd. We assumed these individuals were randomly distributed
throughout the population.

## Landscape data and habitat classification
Land cover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification included nine habitat
types at 30 m resolution. We reclassified the land cover types into three
categories using the R
package `raster` [@Hijmans_2019]: foraging, open, and forest habitats. Foraging habitat consisted of lichen,
open habitat consisted of wetland, rocky barrens, and anthropogenic, while forest habitat consisted of coniferous forest, conifer scrub,
broad leaf forest, and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.
